Improvement of Korean Morphological Analysis System \\Through Transformer-Based Re-Ranking

### 2023-12-04 contents/draft.tex
Elaborate this line with reasons in section 5.5--"The entire morphological analysis model, including the re-ranking model, is not suitable for real-time processing."

    The proposed transformer-based re-ranking technique consistently improved the results of existing morphological analysis models, showcasing its potential to enhance outcomes in the field of Korean morphological analysis.
    These findings suggest that it opens up new possibilities by further refining the results of traditional machine-learning models.
    In a comparative analysis with previous studies, particularly those predominantly focused on the Sejong corpus, we observed performance improvements.
    While direct comparisons are challenging due to slight differences in implementation conditions and evaluation criteria, the proposed dictionary-based morphological analysis model, when coupled with a re-ranking model, achieved a performance comparable to existing research, though not at the latest research results.

    It's worth noting that the entire morphological analysis model, inclusive of the re-ranking model, may not be optimal for real-time processing.
    However, by incorporating cases where ranks are altered through the re-ranking model as feedback to the dictionary-based morphological analysis model, it becomes plausible to achieve near-improved morphological analysis performance.
    The enhanced dictionary-based morphological analysis model can then serve as input to the re-ranking model, fostering iterative improvement in the overall morphological analysis model through this feedback loop.

>>>>

    The proposed transformer-based re-ranking technique consistently improved the results of existing morphological analysis models, showcasing its potential to enhance outcomes in the field of Korean morphological analysis (refer to Table~\ref{tab:differences-with-previous-studies}).
    These findings suggest that it opens up new possibilities by further refining the results of traditional machine-learning models.
    In a comparative analysis with previous studies, particularly those predominantly focused on the Sejong corpus, we observed performance improvements.
    While direct comparisons are challenging due to slight differences in implementation conditions and evaluation criteria, the proposed dictionary-based morphological analysis model, when coupled with a re-ranking model, achieved a performance comparable to existing research, though not at the latest research results.

    It's worth noting that the entire morphological analysis model, inclusive of the two-stage re-ranking model, may not meet the requirements for real-time processing due to various inherent factors.
    The complex re-ranking process evaluates all secondary paths generated by the morphological analysis, consuming significant computational resources and processing power.
    This demand for substantial resources, coupled with the necessity for millisecond-level response times in real-time applications, can introduce unacceptable latency.
    The system's current design may not efficiently handle the continuous data stream and high-throughput needed, potentially leading to user-perceptible delays.

    However, there is potential for performance enhancement.
    By incorporating cases where ranks are altered through the re-ranking model as feedback to the dictionary-based morphological analysis model, it becomes plausible to achieve near-improved morphological analysis performance.
    The enhanced dictionary-based morphological analysis model can then serve as input to the re-ranking model, fostering iterative improvement in the overall morphological analysis model through this feedback loop.
